Homicide Increases in the COVID-19 Era

### 2025-02-20 Draft1.qmd
fixed incomplete code block

abline(h = pretty(weekly_counts$Crimes), v = pretty(weekly_counts$Index), 
       col = "gray", lty = "dotted")

@@

plot(st_geometry(zcta_with_data), 
     col = brewer.pal(9, "Blues")[as.numeric(cut(zcta_with_data$S1903_C03_001E, 
                                                 breaks = 9))], 
     border = 'grey', 
     axes = TRUE, 
     main = "ZCTA Data Colored by Numerical Column", 
     cex.main = 1.5)
```

>>>>

abline(h = pretty(weekly_counts$Crimes), v = pretty(weekly_counts$Index), 
       col = "gray", lty = "dotted")
```

@@

plot(st_geometry(zcta_with_data), 
     col = brewer.pal(9, "Blues")[as.numeric(cut(zcta_with_data$S1903_C03_001E, 
                                                 breaks = 9))], 
     border = 'grey', 
     axes = TRUE, 
     main = "Median Household Income by ", 
     cex.main = 1.5)
```
